\section{Demonstrating the viability of power management attacks}
\label{sec:observing-fault}

In order to demonstrate that a power management attack is possible on this
platform, we attempt to induce a computational fault whilst the SHA-1 hash of
some known data with a known hash is being computed. The aim is for the fault
to result in an incorrect hash being computed. The process is as follows:

\begin{enumerate}
    \item Choose a critical point.
    \item \label{item:stableOPP} Put the system into a stable OPP near the
        chosen critical point.
    \item \label{item:beginSHA} Begin computing the SHA-1 hash of the known data.
    \item \label{item:induceFault} Whilst the hash is being computed,
        \emph{briefly} put the system into an unstable OPP near the chosen
        critical point.
    \item The hash computation ends, and we hope to see an incorrect hash.
\end{enumerate}

We use the data collected in §\ref{sec:unstableOPPs} to choose a stable OPP and
an unstable OPP which both use the same frequency and lie near the
stable–unstable boundary line. The larger the error bars are near this dividing
line for a given frequency, the less clear the distinction between the stable and
unstable regions for that frequency. As such, since the data for 2600~MHz has
the smallest error bar, we will choose OPPs with a frequency of 2600~MHz.
The data we collected shows that the mean critical voltage for 2600~MHz
is $-230.4$~mV. Thus, we decide that the voltage offset of our stable OPP
should be greater than (i.e. more positive than) $-230.4$~mV, and that of the
unstable OPP should be less than (i.e. more negative than) $-230.4$~mV.

In order to perform steps \ref{item:stableOPP} and \ref{item:induceFault}, we
need the ability to alter the voltage scaling parameters of the CPU. Using the
\code{undervolt} utility discussed in §\ref{sec:undervolt} will not afford us the
timing precision required to execute step \ref{item:induceFault} briefly enough
to induce a fault without completely crashing the system. As such, we opt to
write our own program which will alter the voltage scaling paramters in a
suitably brief manner, which requires us to be able to write to the necessary
MSR as discussed in §\ref{sec:undervolt}. This is ultimately done via execution
of the \code{WRMSR} assembly instruction of the x86
architecture~\cite[Vol. 2, §4.4]{intelDevManual}. Since this instruction
must be executed at privilege level 0 or in real-address mode, we cannot
execute it from userspace; we need to do so in kernel mode. We therefore write
a custom kernel module to set the voltage offset at the necessary times.

We take the approach of simply demonstrating that successful fault injection is
possible, rather than developing a fully-formed attack on a program running in
userspace. That is, we could develop a malicious kernel module which lies in
wait until a hash computation begins in userspace, e.g. an
instance of GnuPG's \code{sha1sum} program begins running. Upon detecting that
such a program is running, the kernel module would have to correctly time the
execution of step \ref{item:induceFault} as discussed in~\cite[§3.5]{clkscrew}.
Instead, we take the less complex approach of adapting the source code of
\code{sha1sum}~\cite{gnupgSHA} into a kernel module which, when inserted into
the kernel, performs steps \ref{item:stableOPP}, \ref{item:beginSHA}, and
\ref{item:induceFault}, all in kernel mode. In this way, we can directly add
instructions to the \code{sha1sum} source code to alter the core voltage at
the necessary times. The details of the kernel module we developed for this
purpose, dubbed \code{bad\_sha}, are given in §\ref{sec:bad-sha}. We experiment
with the following parameters:

\begin{itemize}
    \item the voltage offset of the chosen stable OPP;
    \item the voltage offset of the chosen unstable OPP; and
    \item the amount of time in which the unstable OPP is used;
\end{itemize}
and we see that we can successfully induce a fault around $2\%$ of
the time when we use $-225$~mV for the stable OPP, $-234$~mV for the unstable
OPP, and the unstable OPP is in use whilst five (5) 32-bit W-blocks are processed
during the SHA-1 hash computation (where a W-block is defined as in~\cite[§6.1]{rfcSHA}).


