\subsection{Undervolting}

[TBD]

Can we undervolt?

Intel i5-4590, appears to have base voltage of 8.8 volts.

Model-specific registers (MSRs) exist for controlling voltage offset, but no
documentation is provided by Intel regarding this!
No matter — someone (Miha Eleršič) reverse-engineered Throttlestop, and someone
else (George Whewell) provided a nice frontend to change the voltage offsets.
Undervolting is possible in increments of ~1 millivolt.

====

\subsection{Voltage scaling}

Unfortunately, Intel does not seem to provide any documentation for the voltage
scaling interface in their Intel Core processors, though a closed-source
Windows utility called ThrottleStop \cite{throttlestop} exists to control DVFS
parameters. This utility has been reverse-engineered \cite{elersicDoc},
revealing that a model-specific register (MSR) exists to read and write settings
related to voltage scaling. Specifically, the MSR with address 0x150 acts as an
interface for voltage scaling, though this is also not officially documented by
Intel in \cite[Volume 4, §2.13]{intelDevManual}, as would be expected.

Using this interface, it is possible to adjust the voltage offset from the base
voltage in units of $\frac{1}{1024}$ volts. The voltage offset number used by
the MSR is an 11-bit signed integer, thus allowing a maximum voltage offset of
$\pm{1}$ volts. A front-end utility called \code{undervolt} \cite{whewellUndervolt}
has been developed in Python to more easily use the interface described in
\cite{elersicDoc}. We use \code{undervolt} in §\ref{sec:unstableOPPs}.
